---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# JSODPsplines

<!-- badges: start -->
<!-- badges: end -->

JSODPsplines provides tools for estimating derivatives of functions using P-splines, featuring the 'resub' method, a novel approach developed to improve derivative estimation.

## Installation

You can install the released version of JSODPsplines from CRAN with:

``` r
install.packages("JSODPsplines")
```

And the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("username/JSODPsplines")
```

## Example

```{r example}
library(JSODPsplines)

# Basic example
x <- seq(0, 1, length.out = 100)
y <- sin(2 * pi * x) + rnorm(100, sd = 0.1)
x.grid <- seq(0, 1, length.out = 200)

# Estimate the first derivative using the resubstitution method
result <- resub.est(x, y, r = 1, x.grid = x.grid, nseg = 10, pord = 2, bdeg = 3)

# Plot the results
plot(x.grid, result$frg.hat, type = "l", col = "blue", 
     main = "Estimated First Derivative", xlab = "x", ylab = "f'(x)")
lines(x.grid, 2*pi*cos(2*pi*x.grid), col = "red", lty = 2)  # True derivative
legend("topright", legend = c("Estimated", "True"), 
       col = c("blue", "red"), lty = c(1, 2))
```

## Features

JSODPsplines includes the following key functions:

- `resub.est()`: The resubstitution method for derivative estimation
- `pgams()`: Penalized spline derivative estimation
- `naive.est.opt()`: Naive estimation with optimized smoothing parameter
- `plugin.est()`: Plug-in estimation of derivative
- `oracle.est()`: Oracle estimation of derivative (when the true function is known)
- `gcvlambda()`: Generalized cross-validation criterion for smoothing parameter selection

## Citation

If you use this package, please cite:

```{r, eval=FALSE}
citation("JSODPsplines")
```